---
title: "NHG Confidence Intervals for M: Analog to the Clopper-Pearson Method"
author: "Rachel Roggenkemper"
format: html
editor: visual
---

```{r, warning=FALSE}
library(extraDistr)
library(tidyverse)
```

```{r}
# ngh_pmf <- function(x, N, M, m) {
#   # m = # total successes (unknown) - (our notation: M)
#   m_pmf = M  
#   
#   # n = # total failures - (our notation: X = N - M)
#   n_pmf = N - m_pmf 
#   
#   # r = # fixed successes (our notation: m)
#   r_pmf = m   
#   
#   # x = # balls being drawn (our notation: n = m + x) 
#   x_pmf = r_pmf + x
#   
#   return(dnhyper(x = x_pmf, m = m_pmf, n = n_pmf, r = r_pmf))
# }


ngh_pmf <- function(x, N, M, m) {
  numerator = choose(m + x - 1, m - 1) * choose(N - m - x, M - m)
  denominator = choose(N, M)
  result = numerator / denominator
  return(result)
}

# Original (top): ngh_pmf(x = 0, N = 50, M = 50, m = 3) -> R crashes (end points doesn't work for coverage prob)
# New (bottom): ngh_pmf(x = 0, N = 50, M = 50, m = 3) -> 1
```

```{r}
ngh_cdf <- function(x, N, M, m, lower_tail = TRUE) {
  # m = # total successes (unknown) - (our notation: M)
  m_pmf = M  
  
  # n = # total failures - (our notation: X = N - M)
  n_pmf = N - m_pmf 
  
  # r = # fixed successes (our notation: m)
  r_pmf = m   
  
  # x = # balls being drawn (our notation: n = m + x) 
  x_pmf = r_pmf + x
  
  return(pnhyper(q = x_pmf, m = m_pmf, n = n_pmf, r = r_pmf, lower.tail = lower_tail))
}
```

# Confidence Interval for M (total number of successes)

## Testing: m = 3, x = 4, N = 50, Confidence Level = 0.95

### Point Estimate of M

```{r}
# M = 21: Point Estimate of M 

m = 3
x = 4
N = 50
M = 21

data = data.frame(x = seq(0, 50))
data$y = ngh_pmf(x = (data$x), N = N, M = M, m = m)
ggplot(data, aes(x = x, y = y)) +
  geom_line() +
  geom_vline(xintercept = x, color = "red") +
  ggtitle(paste("NGH: M =", M)) +
  xlab("x values") +
  ylab("Density")
```

```{r}
m = 3
x = 4
N = 50
M = 21

data = data.frame(x = seq(0, 50))
data$y = ngh_pmf(x = (data$x), N = N, M = M, m = m)
ggplot(data, aes(x = x, y = y)) +
  geom_line() +
  geom_vline(xintercept = x, color = "red") +
  #ggtitle(paste("NGH: M =", M)) +
  xlab("x") +
  ylab("Probability") +
  theme_minimal() +
  theme(
    legend.position = "none", 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    axis.ticks = element_line(size = 0.5),
    axis.ticks.length = unit(2, "mm"),
    axis.text.x = element_text(margin = margin(t = 5)),
    axis.text.y = element_text(margin = margin(r = 5))) 
```

### Lower Bound

```{r}
# Lower Bound
# M = 6: Area to the left is just over (not under) 0.025 (alpha = 0.05)

m = 3
x = 4
N = 50
M = 6

data = data.frame(x = seq(0, 50))
data$y = ngh_pmf(x = (data$x), N = N, M = M, m = m)
ggplot(data, aes(x = x, y = y)) +
  geom_line() +
  geom_vline(xintercept = x, color = "red") +
  ggtitle(paste("NGH: M =", M)) +
  xlab("x values") +
  ylab("Density")


area_left = ngh_cdf(x = x, N = N, M = M, m = m, lower_tail = TRUE)
area_right = ngh_cdf(x = x - 1, N = N, M = M, m = m, lower_tail = FALSE)
print(paste("Area to the left of n =", m + x, "is:", area_left))
#print(paste("Area to the right of n =", m + x, "is:", area_right))
```

```{r}
m = 3
x = 4
N = 50
M = 6

data = data.frame(x = seq(0, 50))
data$y = ngh_pmf(x = (data$x), N = N, M = M, m = m)
ggplot(data, aes(x = x, y = y)) +
  geom_line() +
  geom_vline(xintercept = x, color = "red") +
  #ggtitle(paste("NGH: M =", M)) +
  xlab("x") +
  ylab("Probability") +
  theme_minimal() +
  theme(
    legend.position = "none", 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    axis.ticks = element_line(size = 0.5),
    axis.ticks.length = unit(2, "mm"),
    axis.text.x = element_text(margin = margin(t = 5)),
    axis.text.y = element_text(margin = margin(r = 5))) 
```

### Upper Bound

```{r}
# Upper Bound
# M = 37: Area to the right is just over (not under) 0.025 (alpha = 0.05)

m = 3
x = 4
N = 50
M = 37

data = data.frame(x = seq(0, 50))
data$y = ngh_pmf(x = (data$x), N = N, M = M, m = m)
# data$y = ngh_pmf(x = (data$x - m), N = N, M = M, m = m)
ggplot(data, aes(x = x, y = y)) +
  geom_line() +
  geom_vline(xintercept = x, color = "red") +
  ggtitle(paste("NGH: M =", M)) +
  xlab("x values") +
  ylab("Density") +
  xlim(0, 10)


area_left = ngh_cdf(x = x, N = N, M = M, m = m, lower_tail = TRUE)
area_right = ngh_cdf(x = x - 1, N = N, M = M, m = m, lower_tail = FALSE)
#print(paste("Area to the left of n =", m + x, "is:", area_left))
print(paste("Area to the right of n =", m + x, "is:", area_right))
```

```{r}
m = 3
x = 4
N = 50
M = 37

data = data.frame(x = seq(0, 50))
data$y = ngh_pmf(x = (data$x), N = N, M = M, m = m)
# data$y = ngh_pmf(x = (data$x - m), N = N, M = M, m = m)
ggplot(data, aes(x = x, y = y)) +
  geom_line() +
  geom_vline(xintercept = x, color = "red") +
  #ggtitle(paste("NGH: M =", M)) +
  xlab("x") +
  ylab("Probability") +
  theme_minimal() +
  theme(
    legend.position = "none", 
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    axis.ticks = element_line(size = 0.5),
    axis.ticks.length = unit(2, "mm"),
    axis.text.x = element_text(margin = margin(t = 5)),
    axis.text.y = element_text(margin = margin(r = 5))) +
  scale_x_continuous(limits = c(0, 10), breaks = c(0, 5, 10))
```

## Confidence Interval Function

```{r}
NGH_CI_Exact_Method <- function(m, x, N, conf_level = 0.95) {
  target_probability = (1 - conf_level) / 2
  
  # Speical End Cases: When x in N-m to N
  if ((x >= (N - m)) & (x <= N)) {
    lower_bound = N - x
    upper_bound = N - x
  }
  
  else {
    # Initilaizing lower and upper bound
    lower_bound = m
    upper_bound = N
    
    # Find lower bound: iterating until the area to the left is greater than or equal 
    for (M in m:N) {
      area_left = ngh_cdf(x = x, N = N, M = M, m = m, lower_tail = TRUE)
      
      #if (area_left == target_probability) {
      if (isTRUE(all.equal(area_left, target_probability))) {
        lower_bound = M
        break
      }
      
      else if (area_left > target_probability) {
        lower_bound = M
        break
      }
    }
  
    # Find upper bound: iterating until the area to the right is greater than or equal 
    for (M in N:m) {
      area_right = ngh_cdf(x = x - 1, N = N, M = M, m = m, lower_tail = FALSE)
      
      #if (area_right == target_probability) {
      if (isTRUE(all.equal(area_right, target_probability))) {
        upper_bound = M
        break
      }
      
      else if (area_right > target_probability) {
        upper_bound = M 
        break
      }
    }
  }

  
  CL = (conf_level) * 100
  return(cat(CL, "% Confidence Interval for M: [", lower_bound, ",", upper_bound, "]\n"))
}
```

### Testing Confidence Interval Function

```{r}
# Debany: n = 3 (m + x)
# Debany CI: [15.3488, 49.9993]
m = 3
x = 0
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

```{r}
# Debany: n = 4 (m + x)
# Debany CI: [10.4493, 48.9993]
m = 3
x = 1
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

```{r}
# Debany: n = 5 (m + x)
# Debany CI: [8.0846, 46.1811]
m = 3
x = 2
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

```{r}
# Debany: n = 6 (m + x)
# Debany CI: [6.6705, 41.9156]
m = 3
x = 3
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

```{r}
# Debany: n = 7 (m + x)
# Debany CI: [5.7249, 37.8620]
m = 3
x = 4
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

```{r}
# Debany: n = 8 (m + x)
# Debany CI: [5.0489, 34.2853]
m = 3
x = 5
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

```{r}
# Debany: n = 9 (m + x)
# Debany CI: [4.5421, 31.1894]
m = 3
x = 6
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

```{r}
# Debany: n = 10 (m + x)
# Debany CI: [4.1493, 28.5182]
m = 3
x = 7
N = 50
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

### Cal Poly COVID Example: CI for M

```{r}
set.seed(8)  

# Total number of students
N = 21778
# Number of positive students
M = 1293
# Number of positives to observe in sampling
m = 20

# Create a vector representing the population
population = c(rep(1, M), rep(0, N - M))  # 1 represents positive, 0 represents negative

# Sample until we get 20 positives
sample_positives = function(population, m) {
  positives_count = 0
  negatives_count = 0
  total_samples = 0
  
  while (positives_count < m) {
    sample = sample(population, 1)
    total_samples = total_samples + 1
    if (sample == 1) {
      positives_count = positives_count + 1
    } else {
      negatives_count = negatives_count + 1
    }
  }
  
  return(list(total_samples = total_samples, negatives_count = negatives_count))
}

# Run the sampling
result = sample_positives(population, m)
total_samples = result$total_samples
negatives_count = result$negatives_count

cat("Total samples taken to get 20 positives: ", total_samples, "\n")
cat("Number of negatives observed before getting 20 positives: ", negatives_count, "\n")
```

```{r}
m = 20
x = 448
N = 21778
conf_level = 0.95

NGH_CI_Exact_Method(m, x, N, conf_level)
```

# Coverage Probability for M

```{r}
# Finding the confidence interals: same principle as function above, just reformatted output
CI_cov_prob <- function(N, m, conf_level = 0.95) {
  target_probability = (1 - conf_level) / 2
  
  #results = data.frame(x = 0:(N - m), lower_bound = NA, upper_bound = NA)
  results = data.frame(x = 0:(N), lower_bound = NA, upper_bound = NA)
  
  #for (xi in 0:(N - m)) {
  for (xi in 0:(N)) {
    # Speical End Cases: When x in N-m to N
    if ((xi >= (N - m)) & (xi <= N)) {
      lower_bound = N - xi
      upper_bound = N - xi
    }
    
    else {
      lower_bound = m
      upper_bound = N
      
      # Find lower bound
      for (M in m:N) {
        area_left = ngh_cdf(x = xi, N = N, M = M, m = m, lower_tail = TRUE)
        
        #if (area_left == target_probability) {
        if (isTRUE(all.equal(area_left, target_probability))) {
          lower_bound = M
          break
        }
        
        else if (area_left > target_probability) {
          lower_bound = M
          break
        }
      }
    
      # Find upper bound
      for (M in N:m) {
        area_right = ngh_cdf(x = xi - 1, N = N, M = M, m = m, lower_tail = FALSE)
        
        #if (area_right == target_probability) {
        if (isTRUE(all.equal(area_right, target_probability))) {
          upper_bound = M
          break
        }
        
        else if (area_right > target_probability) {
          upper_bound = M
          break
        }
      }
    }
    
    # Store the results
    results[xi + 1, "lower_bound"] = lower_bound
    results[xi + 1, "upper_bound"] = upper_bound
  }
  
  return(results)
}
```

```{r}
CI_cov_prob_vec <- function(N, m, conf_level = 0.95) {
  target_probability <- (1 - conf_level) / 2
  
  # Pre-allocate storage
  x_values      <- seq.int(0, N)
  lower_bounds  <- numeric(length(x_values))
  upper_bounds  <- numeric(length(x_values))
  
  # Loop once over all x
  for (i in seq_along(x_values)) {
    xi <- x_values[i]
    
    if (xi >= (N - m) && xi <= N) {
      # Special case
      lower_bounds[i] <- N - xi
      upper_bounds[i] <- N - xi
    } else {
      # Defaults
      lb <- m
      ub <- N
      
      # Find lower bound
      for (M_val in seq.int(m, N)) {
        area_left <- ngh_cdf(x = xi, N = N, M = M_val, m = m, lower_tail = TRUE)
        if (isTRUE(all.equal(area_left, target_probability)) ||
            (area_left > target_probability)) {
          lb <- M_val
          break
        }
      }
      
      # Find upper bound
      for (M_val in seq.int(N, m, by = -1)) {
        area_right <- ngh_cdf(x = xi - 1, N = N, M = M_val, m = m, lower_tail = FALSE)
        if (isTRUE(all.equal(area_right, target_probability)) ||
            (area_right > target_probability)) {
          ub <- M_val
          break
        }
      }
      
      lower_bounds[i] <- lb
      upper_bounds[i] <- ub
    }
  }
  
  # Build the final data frame
  results <- data.frame(
    x           = x_values,
    lower_bound = lower_bounds,
    upper_bound = upper_bounds
  )
  return(results)
}
```

```{r}
# CI_cov_prob(N = 20, m = 3, conf_level = 0.95)
# CI_cov_prob_vec(N = 20, m = 3, conf_level = 0.95)
```

```{r}
coverage_prob <- function(M, N, m, conf_level = 0.95) {
  # if (M < m || M > N) {
  #   stop("Invalid parameters: Ensure M >= m, M <= N")
  #   }
  
  # Calculates all confidence intervals 
  ci_results = CI_cov_prob(N, m, conf_level)
  
  # Finds all x's where M is in the confidence interval 
  covered_x = ci_results %>% 
    filter(lower_bound <= M & upper_bound >= M) %>% 
    pull(x)
  
  if (length(covered_x) == 0) {
    return(data.frame(M = M, coverage_prob = NA, min_x = NA, max_x = NA))
  }
  
  # Finds the min and max of covered x's to know which lines to connect in plot
  min_x = min(covered_x, na.rm = TRUE)
  max_x = max(covered_x, na.rm = TRUE)
  
  # Sums the probabilities (pmf's) of all x's where M is in the CI 
  #total_prob = sum(sapply(covered_x, function(x) ngh_pmf(x, N, M, m)))
  total_prob = sum(unlist(lapply(covered_x, function(x) ngh_pmf(x, N, M, m))))
  return(data.frame(M = M, coverage_prob = total_prob, min_x = min_x, max_x = max_x))
}
```

```{r}
# N = 200
# m = 20
# conf_level = 0.95
# M_values = m:N
# 
# coverage_df = do.call(rbind, lapply(M_values, function(M) coverage_prob(M, N, m, conf_level)))
# mean(coverage_df$coverage_prob)
```

### Plot for interplay between a cpf and resulting intervals

### N = 15, m = 3, Confidence Level = 0.95

```{r}
N = 15
m = 3
conf_level = 0.95
M_values = 0:N



coverage_df = do.call(rbind, lapply(M_values, function(M) coverage_prob(M, N, m, conf_level)))

# Create a group column for consistent min_x and max_x
coverage_df = coverage_df %>%
  mutate(group = cumsum(c(1, diff(min_x) != 0 | diff(max_x) != 0)))



ci_results = CI_cov_prob(N, m, conf_level) %>%
  filter(x <= 12)

y_axis = seq(from = 0.94, by = -0.01, length.out = 13)

ci_results$y_axis = y_axis



# Create the plot
ggplot() +
  geom_line(data = coverage_df, aes(x = M, y = coverage_prob, group = group)) +
  geom_point(data = coverage_df, aes(x = M, y = coverage_prob, group = group)) +
  labs(x = "M", y = "Coverage Probability") +
  geom_hline(yintercept = conf_level, color = "red", linetype = "dashed") +
  scale_y_continuous(breaks = c(0.95, 1), limits = c(0.815, 1.015)) +
  scale_x_continuous(breaks = 3:15, limits = c(2.8, 15.1)) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    axis.ticks = element_line(size = 0.5),
    axis.ticks.length = unit(2, "mm"),
    axis.text.x = element_text(margin = margin(t = 5)),
    axis.text.y = element_text(margin = margin(r = 5))) +
  annotate("text", 
           x = 2.8, 
           y = 0.99,
           label = paste0("3-12"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 3.8, 
           y = 1,
           label = paste0("1-11"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 4.8, 
           y = 0.97,
           label = paste0("1-9"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 5.8, 
           y = 1,
           label = paste0("0-8"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 6.8, 
           y = 1.005,
           label = paste0("0-7"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 7.8, 
           y = 1.005,
           label = paste0("0-6"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 8.8, 
           y = 1.005,
           label = paste0("0-5"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 9.8, 
           y = 1.005,
           label = paste0("0-4"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 10.8, 
           y = 1,
           label = paste0("0-3"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 12.1, 
           y = 1,
           label = paste0("0-2"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) + 
  annotate("text", 
           x = 13.8, 
           y = 1.009,
           label = paste0("0-1"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  annotate("text", 
           x = 14.8, 
           y = 1.009,
           label = paste0("0-0"), 
           angle = 0, hjust = 0, vjust = 1, size = 3.25) +
  geom_errorbarh(data = ci_results, 
                aes(y = y_axis, xmin = lower_bound, xmax = upper_bound), width = 0.2) +
  geom_label(aes(x = 10.5, y = 0.943, label = "CI(0)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) + 
  geom_label(aes(x = 9, y = 0.933, label = "CI(1)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) +
  geom_label(aes(x = 8, y = 0.923, label = "CI(2)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) +
  geom_label(aes(x = 7, y = 0.913, label = "CI(3)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) +
  geom_label(aes(x = 6.5, y = 0.903, label = "CI(4)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) +
  geom_label(aes(x = 6, y = 0.893, label = "CI(5)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) +
  geom_label(aes(x = 5.5, y = 0.883, label = "CI(6)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) +
  geom_label(aes(x = 4.7, y = 0.873, label = "CI(7)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) +
  geom_label(aes(x = 4.2, y = 0.863, label = "CI(8)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) + 
  geom_label(aes(x = 3.7, y = 0.853, label = "CI(9)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) + 
  geom_label(aes(x = 3.08, y = 0.843, label = "CI(10)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) + 
  geom_label(aes(x = 3.08, y = 0.833, label = "CI(11)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1) + 
  geom_label(aes(x = 3.05, y = 0.823, label = "CI(12)"), 
             color = "black", fill = "white", 
             label.size = 0.4, size = 2.5, hjust = 0, vjust = 1)
```

### N = 20, m = 3, Confidence Level = 0.95

Coverage Probability = 0 when M = 0, 1, 2

```{r}
N = 20
m = 3
conf_level = 0.95
M_values = 0:N

coverage_df = do.call(rbind, lapply(M_values, function(M) coverage_prob(M, N, m, conf_level)))

# Create a group column for consistent min_x and max_x
# The group column assigns a unique group number whenever there is a change in min_x or max_x values
# cumsum is used to create a cumulative sum that increments the group number whenever there is a
# change in min_x or max_x
coverage_df = coverage_df %>%
  mutate(group = cumsum(c(1, diff(min_x) != 0 | diff(max_x) != 0)))

ggplot(coverage_df, aes(x = M, y = coverage_prob, group = group)) +
  geom_line() +
  geom_point() +
  labs(x = "M", y = "Coverage Probability of M") +
  geom_hline(yintercept = conf_level, color = "red") +
  # ylim(0, 1) +
  ylim(conf_level - 0.005, 1) +
  theme_minimal()
```

### N = 50, m = 3, Confidence Level = 0.95

Coverage Probability = 0 when M = 0, 1, 2

```{r}
N = 50
m = 3
conf_level = 0.95
M_values = 0:N

coverage_df = do.call(rbind, lapply(M_values, function(M) coverage_prob(M, N, m, conf_level)))

# Create a group column for consistent min_x and max_x
# The group column assigns a unique group number whenever there is a change in min_x or max_x values
# cumsum is used to create a cumulative sum that increments the group number whenever there is a
# change in min_x or max_x
coverage_df = coverage_df %>%
  mutate(group = cumsum(c(1, diff(min_x) != 0 | diff(max_x) != 0)))

ggplot(coverage_df, aes(x = M, y = coverage_prob, group = group)) +
  geom_line() +
  geom_point() +
  labs(x = "M", y = "Coverage Probability of M") +
  geom_hline(yintercept = conf_level, color = "red") +
  ylim(conf_level - 0.005, 1) +
  theme_minimal()
```

### N = 100, m = 3, Confidence Level = 0.95

Coverage Probability = 0 when M = 0, 1, 2

```{r}
N = 100
m = 3
conf_level = 0.95
M_values = 0:N

coverage_df = do.call(rbind, lapply(M_values, function(M) coverage_prob(M, N, m, conf_level)))

# Create a group column for consistent min_x and max_x
# The group column assigns a unique group number whenever there is a change in min_x or max_x values
# cumsum is used to create a cumulative sum that increments the group number whenever there is a
# change in min_x or max_x
coverage_df = coverage_df %>%
  mutate(group = cumsum(c(1, diff(min_x) != 0 | diff(max_x) != 0)))

ggplot(coverage_df, aes(x = M, y = coverage_prob, group = group)) +
  geom_line() +
  geom_point() +
  labs(x = "M", y = "Coverage Probability of M") +
  geom_hline(yintercept = conf_level, color = "red") +
  ylim(conf_level - 0.005, 1) +
  theme_minimal()
```

### Testing

```{r}
test <- function(M, N, m, conf_level = 0.95) {
  # if (M < m || M > N) {
  #   stop("Invalid parameters: Ensure M >= m, M <= N")
  #   }
  
  # Calculates all confidence intervals 
  ci_results = CI_cov_prob(N, m, conf_level)
  
  # Finds all x's where M is in the confidence interval 
  covered_x = ci_results %>% 
    filter(lower_bound <= M & upper_bound >= M) %>% 
    pull(x)
  
  # Finds the min and max of covered x's to know which lines to connect in plot
  min_x = min(covered_x)
  max_x = max(covered_x)
  
  # Sums the probabilities (pmf's) of all x's where M is in the CI 
  #total_prob = sum(sapply(covered_x, function(x) ngh_pmf(x, N, M, m)))
  total_prob = sum(unlist(lapply(covered_x, function(x) ngh_pmf(x, N, M, m))))
  return(covered_x)
}

# test(M = 0, N = 50, m = 3)
# test(M = 1, N = 50, m = 3)
# test(M = 2, N = 50, m = 3)
# test(M = 3, N = 50, m = 3)
# test(M = 4, N = 50, m = 3)
# test(M = 5, N = 50, m = 3)
# test(M = 6, N = 50, m = 3)
# test(M = 7, N = 50, m = 3)
# test(M = 8, N = 50, m = 3)
# test(M = 9, N = 50, m = 3)
# test(M = 10, N = 50, m = 3)
# test(M = 11, N = 50, m = 3)
# test(M = 12, N = 50, m = 3)
# test(M = 13, N = 50, m = 3)
# test(M = 14, N = 50, m = 3)
# test(M = 15, N = 50, m = 3)
# test(M = 16, N = 50, m = 3)
# test(M = 17, N = 50, m = 3)
# test(M = 18, N = 50, m = 3)
# test(M = 19, N = 50, m = 3)
# test(M = 20, N = 50, m = 3)
# test(M = 21, N = 50, m = 3)
# test(M = 22, N = 50, m = 3)
# test(M = 23, N = 50, m = 3)
# test(M = 24, N = 50, m = 3)
# test(M = 25, N = 50, m = 3)
# test(M = 26, N = 50, m = 3)
# test(M = 27, N = 50, m = 3)
# test(M = 28, N = 50, m = 3)
# test(M = 29, N = 50, m = 3)
# test(M = 30, N = 50, m = 3)
# test(M = 31, N = 50, m = 3)
# test(M = 32, N = 50, m = 3)
# test(M = 33, N = 50, m = 3)
# test(M = 34, N = 50, m = 3)
# test(M = 35, N = 50, m = 3)
# test(M = 36, N = 50, m = 3)
# test(M = 37, N = 50, m = 3)
# test(M = 38, N = 50, m = 3)
# test(M = 39, N = 50, m = 3)
# test(M = 40, N = 50, m = 3)
# test(M = 41, N = 50, m = 3)
# test(M = 42, N = 50, m = 3)
# test(M = 43, N = 50, m = 3)
# test(M = 44, N = 50, m = 3)
# test(M = 45, N = 50, m = 3)
# test(M = 46, N = 50, m = 3)
# test(M = 47, N = 50, m = 3)
# test(M = 48, N = 50, m = 3)
# test(M = 49, N = 50, m = 3)
#test(M = 50, N = 50, m = 3)
```

```{r}
# test_CI = CI_cov_prob(N = 50, m = 3) 
# test_CI
```
