---
title: "NHG vs HG: Simulating Point Estimates"
author: "Rachel Roggenkemper"
format: html
editor: visual
---

# Set-Up

```{r}
#| label: load libraries
#| message: false

library(tidyverse)
library(extraDistr)
```

```{r}
#| label: custom ngh sampling function 

r_ngh <- function(num_obs, N, M, m) {
  # m = # total successes (unknown) - (our notation: M)
  m_pmf = M  
  
  # n = # total failures - (our notation: X = N - M)
  n_pmf = N - m_pmf 
  
  # r = # fixed successes (our notation: m)
  r_pmf = m   

  return(rnhyper(num_obs, m = m_pmf, n = n_pmf, r = r_pmf))
}
```

# Simulate Point Estimates (fix N, M, m)

## Function

```{r}
#| label: point estimate simulation function (m)

simulate_point_estimate_m <- function(simulations = 1000, true_N, true_M, m) {
  
  # Initializing results data frame
  results <- data.frame(sim = 1:simulations,
                        est_N_HG = numeric(simulations),
                        est_M_HG = numeric(simulations),
                        est_N_NHG = numeric(simulations),
                        est_M_NHG = numeric(simulations)) 

  # Simulation loop
  for (i in 1:simulations) {
    # Sample from Negative Hypergeometric
    x_NHG <- r_ngh(1, true_N, true_M, m)  # Number of failures before m successes
    n_NHG <- m + x_NHG  # Total number of items sampled

    # Sample from Hypergeometric
    m_HG <- rhyper(1, true_M, true_N - true_M, n_NHG)  # Number of successes observed

    # Point estimates for Hypergeometric (handle cases where m_HG = 0 or NA)
    if (is.na(m_HG) || m_HG == 0) {
      est_N_HG <- NA
      est_M_HG <- NA
    } else {
      est_N_HG <- (true_M * n_NHG) / m_HG
      est_M_HG <- (true_N * m_HG) / n_NHG
    }

    # Point estimates for Negative Hypergeometric
    est_N_NHG <- (true_M * n_NHG) / m
    est_M_NHG <- (true_N * m) / n_NHG

    # Store results
    results[i, ] <- c(i, est_N_HG, est_M_HG, est_N_NHG, est_M_NHG)
  }

  # Calculate MSE for estimates
  mse_N_HG <- mean((results$est_N_HG - true_N)^2, na.rm = TRUE)
  mse_M_HG <- mean((results$est_M_HG - true_M)^2, na.rm = TRUE)
  mse_N_NHG <- mean((results$est_N_NHG - true_N)^2, na.rm = TRUE)
  mse_M_NHG <- mean((results$est_M_NHG - true_M)^2, na.rm = TRUE)
  
  # Calculate MSE ratios
  mse_N_ratio <- mse_N_NHG / mse_N_HG
  mse_M_ratio <- mse_M_NHG / mse_M_HG

  # Return results as a list
  return(list(
    MSE_Hypergeometric = list(N = mse_N_HG, M = mse_M_HG),
    MSE_Negative_Hypergeometric = list(N = mse_N_NHG, M = mse_M_NHG),
    MSE_ratio = list(mse_N_ratio = mse_N_ratio, mse_M_ratio = mse_M_ratio)
  ))
}
```

## Testing Function

```{r}
#| label: testing function (m)

set.seed(814)

true_N = 1000
true_M = 300
m = 20

results <- simulate_point_estimate_m(simulations = 10000, true_N, true_M, m)

cat("\nMSE for Hypergeometric estimates:\n")
cat(sprintf("N: %.4f\n", results$MSE_Hypergeometric$N))
cat(sprintf("M: %.4f\n", results$MSE_Hypergeometric$M))

cat("\nMSE for Negative Hypergeometric estimates:\n")
cat(sprintf("N: %.4f\n", results$MSE_Negative_Hypergeometric$N))
cat(sprintf("M: %.4f\n", results$MSE_Negative_Hypergeometric$M))

cat("\nMSE Ratios:\n")
cat(sprintf("N: %.4f\n", results$MSE_ratio$mse_N_ratio))
cat(sprintf("M: %.4f\n", results$MSE_ratio$mse_M_ratio))
```

## Simulating Combinations of N, M, and m

```{r}
#| label: simulating multiple combinations of N, M, and m
#| warning: false
#| eval: false

set.seed(814)

parameters <- data.frame(
  N = c(
    rep(100, 12),  
    rep(500, 15),  
    rep(1000, 15) 
  ),
  M = c(
    rep(25, 3), rep(50, 4), rep(75, 5),      
    rep(100, 5), rep(250, 5), rep(400, 5),   
    rep(250, 5), rep(500, 5), rep(750, 5)   
  ),
  m = c(
    5, 10, 15, 5, 10, 15, 25, 5, 10, 15, 25, 40,   
    5, 10, 25, 40, 50, 10, 20, 30, 40, 50, 10, 20, 50, 60, 75,  
    5, 10, 25, 40, 50, 10, 20, 30, 40, 50, 10, 20, 50, 60, 75  
  )
)


results_df <- data.frame()

for (i in 1:nrow(parameters)) {
  true_N <- parameters$N[i]
  true_M <- parameters$M[i]
  m <- parameters$m[i]
  
  result <- simulate_point_estimate_m(simulations = 10000, 
                                    true_N = true_N, 
                                    true_M = true_M, 
                                    m = m)
  
  results_df <- rbind(
    results_df,
    data.frame(
      N = true_N,
      M = true_M,
      m = m,
      MSE_HG_N = result$MSE_Hypergeometric$N,
      MSE_NHG_N = result$MSE_Negative_Hypergeometric$N,
      Diff_MSE_N = result$MSE_Hypergeometric$N - result$MSE_Negative_Hypergeometric$N,
      MSE_HG_M = result$MSE_Hypergeometric$M,
      MSE_NHG_M = result$MSE_Negative_Hypergeometric$M,
      Diff_MSE_M = result$MSE_Hypergeometric$M - result$MSE_Negative_Hypergeometric$M,
      M_over_N = true_M / true_N,
      m_over_M = m / true_M
    )
  )
}
```

```{r}
#| label: simulating random combinations of N, M, and m
#| warning: false
#| eval: false

set.seed(814)

num_combinations <- 50  
parameters <- data.frame(
  N = sample(seq(100, 2000, by = 100), num_combinations, replace = TRUE), 
  M = NA, 
  m = NA   
)

parameters$M <- sapply(parameters$N, function(N) sample(seq(10, N, by = 10), 1))  
parameters$m <- sapply(parameters$M, function(M) sample(seq(5, M/5, by = 1), 1))   

results_df_2 <- data.frame()

for (i in 1:nrow(parameters)) {
  true_N <- parameters$N[i]
  true_M <- parameters$M[i]
  m <- parameters$m[i]
  
  result <- simulate_point_estimate_m(simulations = 10000, 
                                    true_N = true_N, 
                                    true_M = true_M, 
                                    m = m)
  
  results_df_2 <- rbind(
    results_df_2,
    data.frame(
      N = true_N,
      M = true_M,
      m = m,
      MSE_HG_N = result$MSE_Hypergeometric$N,
      MSE_NHG_N = result$MSE_Negative_Hypergeometric$N,
      Diff_MSE_N = result$MSE_Hypergeometric$N - result$MSE_Negative_Hypergeometric$N,
      MSE_HG_M = result$MSE_Hypergeometric$M,
      MSE_NHG_M = result$MSE_Negative_Hypergeometric$M,
      Diff_MSE_M = result$MSE_Hypergeometric$M - result$MSE_Negative_Hypergeometric$M,
      M_over_N = true_M / true_N,
      m_over_M = m / true_M
    )
  )
}
```

```{r}
#| eval: false

write.csv(results_df, file.path("/Users/rachelroggenkemper/Documents/NegativeHypergeometric/Simulation_Comparison", "comp_1.csv"), row.names = FALSE)

write.csv(results_df_2, file.path("/Users/rachelroggenkemper/Documents/NegativeHypergeometric/Simulation_Comparison", "comp_2.csv"), row.names = FALSE)
```

Note: Difference (MSE) = HG - NHG

-   Diff \> 0 (positive) -\> HG \> NHG = NHG performs better (lower MSE)

-   Diff \< 0 (negative) -\> HG \< NHG = HG performs better (lower MSE)

Note: Ratio (MSE) = NHG / HG

-   Ratio \> 1 -\> HG \< NHG = HG performs better (lower MSE)

-   Ratio \< 1 -\> HG \> NHG = NHG performs better (lower MSE)

### Observations and Trends

1.  **Performance of NHG vs. HG for (N)**:
    -   **NHG Performs Better (Positive Diff)**:
        -   When the difference is positive ((Diff_MSE_N \> 0)), NHG has lower MSE. This is more likely when:
            -   \(N\) and (M) are large (e.g., (N \> 500, M \> 100)).
            -   The sampling fraction ((M / N)) is small, meaning the population of successes is sparse.
            -   \(m\) is small relative to (M) (e.g., (m / M \< 0.5)), indicating fewer successes are observed relative to the total successes.
    -   **HG Performs Better (Negative Diff)**:
        -   When the difference is negative ((Diff_MSE_N \< 0)), HG has lower MSE. This happens when:
            -   \(N\) and (M) are small (e.g., (N \< 500, M \< 100)).
            -   The sampling fraction ((M / N)) is large, meaning the population of successes is denser.
            -   \(m\) is large relative to (M) (e.g., (m / M \> 0.5)).
2.  **Performance of NHG vs. HG for (M)**:
    -   **NHG Performs Better (Positive Diff)**:
        -   When the difference is positive ((Diff_MSE_M \> 0)), NHG has lower MSE. This is observed when:
            -   \(N\) is large, and (M) is a small fraction of (N) (e.g., (M / N \< 0.5)).
            -   The number of observed successes ((m)) is relatively small (e.g., (m / M \< 0.5)).
    -   **HG Performs Better (Negative Diff)**:
        -   When the difference is negative ((Diff_MSE_M \< 0)), HG has lower MSE. This occurs when:
            -   \(m\) is close to (M) (e.g., (m / M approximately = 1)).
            -   \(M\) is a large fraction of (N), and the population of successes is denser.
3.  **Impact of the Ratio (M / N)**:
    -   NHG outperforms HG (positive difference) as (M / N) decreases, especially when (M) is a small proportion of the population size (N).
    -   HG performs better (negative difference) as (M / N) increases, meaning the population contains a higher density of successes.
4.  **Impact of the Ratio (m / M)**:
    -   NHG performs better (positive difference) when (m / M) is small, as the Negative Hypergeometric distribution is specifically designed for cases where the number of successes ((m)) is fixed.
    -   HG performs better (negative difference) as (m / M) approaches 1, benefiting from its fixed sample size ((n)).

### Summary Interpretation

-   **NHG excels** in situations with:
    -   Large populations ((N)), sparse successes ((M / N) small), and smaller observed successes ((m / M) small).
-   **HG excels** when:
    -   The population has a higher density of successes ((M / N) large), and the observed successes ((m / M)) are closer to the total successes.

## Exploratory Data Analysis

```{r}
#| label: combining above results into one dataset (m)
#| message: false

results_df <- read_csv(here::here("Simulation_Comparison", "comp_1.csv"))
results_df_2 <- read_csv(here::here("Simulation_Comparison", "comp_2.csv"))

combined_results <- bind_rows(results_df, results_df_2)
```

```{r}
#| warning: false

# Plot 1: Diff_MSE_N vs. M/N
ggplot(combined_results, aes(x = M_over_N, y = Diff_MSE_N, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(
    title = "Difference in MSE (N): NHG vs. HG by M/N",
    x = "M / N (Success Fraction in Population)",
    y = "Diff_MSE_N (HG - NHG)",
    color = "N"
  ) 

ggplot(combined_results, aes(x = M_over_N, y = Diff_MSE_N, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Difference in MSE (N): NHG vs. HG by M/N",
    x = "M / N (Success Fraction in Population)",
    y = "Diff_MSE_N (HG - NHG)",
    color = "N"
  ) 
```

```{r}
#| warning: false

# Plot 2: Diff_MSE_N vs. m/M
ggplot(combined_results, aes(x = m_over_M, y = Diff_MSE_N, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(
    title = "Difference in MSE (N): NHG vs. HG by m/M",
    x = "m / M (Observed Success Fraction)",
    y = "Diff_MSE_N (HG - NHG)",
    color = "N"
  ) 

ggplot(combined_results, aes(x = m_over_M, y = Diff_MSE_N, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Difference in MSE (N): NHG vs. HG by m/M",
    x = "m / M (Observed Success Fraction)",
    y = "Diff_MSE_N (HG - NHG)",
    color = "N"
  ) 
```

```{r}
#| warning: false

# Plot 3: Diff_MSE_M vs. M/N
ggplot(combined_results, aes(x = M_over_N, y = Diff_MSE_M, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(
    title = "Difference in MSE (M): NHG vs. HG by M/N",
    x = "M / N (Success Fraction in Population)",
    y = "Diff_MSE_M (HG - NHG)",
    color = "N"
  )

ggplot(combined_results, aes(x = M_over_N, y = Diff_MSE_M, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Difference in MSE (M): NHG vs. HG by M/N",
    x = "M / N (Success Fraction in Population)",
    y = "Diff_MSE_M (HG - NHG)",
    color = "N"
  )
```

```{r}
#| warning: false

# Plot 4: Diff_MSE_M vs. m/M
ggplot(combined_results, aes(x = m_over_M, y = Diff_MSE_M, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(
    title = "Difference in MSE (M): NHG vs. HG by m/M",
    x = "m / M (Observed Success Fraction)",
    y = "Diff_MSE_M (HG - NHG)",
    color = "N"
  ) 

ggplot(combined_results, aes(x = m_over_M, y = Diff_MSE_M, color = as.factor(N))) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Difference in MSE (M): NHG vs. HG by m/M",
    x = "m / M (Observed Success Fraction)",
    y = "Diff_MSE_M (HG - NHG)",
    color = "N"
  ) 
```

## The Plot.

### Simulating 

```{r}
#| eval: false

set.seed(818)

# Create an empty data frame to store all simulation results
results_all <- data.frame()

# Number of simulations per combination
n_sim <- 10000

# Loop over each value of m and its corresponding N and M combinations
for (m_val in c(5, 10, 15, 20)) {
  
  if (m_val == 5) {
    N_vals <- c(50, 75, 100, 250, 500, 750, 1000)
    for (N in N_vals) {
      # Define M values based on N for m = 5
      if (N == 50) {
        M_vec <- seq(10, 30, by = 5)
      } else if (N == 75) {
        M_vec <- seq(10, 55, by = 5)
      } else if (N == 100) {
        M_vec <- seq(10, 60, by = 5)
      } else if (N == 250) {
        M_vec <- seq(10, 150, by = 10)
      } else if (N == 500) {
        M_vec <- seq(10, 300, by = 10)
      } else if (N == 750) {
        M_vec <- seq(10, 450, by = 10)
      } else if (N == 1000) {
        M_vec <- seq(10, 600, by = 10)
      }
      
      for (M in M_vec) {
        # Run the simulation for the current combination
        sim_out <- simulate_point_estimate_m(simulations = n_sim,
                                             true_N = N,
                                             true_M = M,
                                             m = m_val)
        # Append the simulation summary to the results data frame
        results_all <- rbind(results_all,
                             data.frame(m = m_val,
                                        true_N = N,
                                        true_M = M,
                                        mse_N_HG = sim_out$MSE_Hypergeometric$N,
                                        mse_M_HG = sim_out$MSE_Hypergeometric$M,
                                        mse_N_NHG = sim_out$MSE_Negative_Hypergeometric$N,
                                        mse_M_NHG = sim_out$MSE_Negative_Hypergeometric$M,
                                        mse_N_ratio = sim_out$MSE_ratio$mse_N_ratio,
                                        mse_M_ratio = sim_out$MSE_ratio$mse_M_ratio))
      }
    }
    
  } else if (m_val == 10) {
    N_vals <- c(150, 250, 500, 750, 1000)
    for (N in N_vals) {
      # Define M values based on N for m = 10
      if (N == 150) {
        M_vec <- seq(20, 60, by = 10)
      } else if (N == 250) {
        M_vec <- seq(20, 150, by = 10)
      } else if (N == 500) {
        M_vec <- seq(20, 300, by = 10)
      } else if (N == 750) {
        M_vec <- seq(20, 450, by = 10)
      } else if (N == 1000) {
        M_vec <- seq(20, 600, by = 10)
      }
      
      for (M in M_vec) {
        sim_out <- simulate_point_estimate_m(simulations = n_sim,
                                             true_N = N,
                                             true_M = M,
                                             m = m_val)
        results_all <- rbind(results_all,
                             data.frame(m = m_val,
                                        true_N = N,
                                        true_M = M,
                                        mse_N_HG = sim_out$MSE_Hypergeometric$N,
                                        mse_M_HG = sim_out$MSE_Hypergeometric$M,
                                        mse_N_NHG = sim_out$MSE_Negative_Hypergeometric$N,
                                        mse_M_NHG = sim_out$MSE_Negative_Hypergeometric$M,
                                        mse_N_ratio = sim_out$MSE_ratio$mse_N_ratio,
                                        mse_M_ratio = sim_out$MSE_ratio$mse_M_ratio))
      }
    }
    
  } else if (m_val == 15) {
    N_vals <- c(250, 500, 750, 1000)
    for (N in N_vals) {
      # Define M values based on N for m = 15
      if (N == 250) {
        M_vec <- seq(25, 100, by = 10)
      } else if (N == 500) {
        M_vec <- seq(25, 300, by = 10)
      } else if (N == 750) {
        M_vec <- seq(25, 450, by = 10)
      } else if (N == 1000) {
        M_vec <- seq(25, 600, by = 10)
      }
      
      for (M in M_vec) {
        sim_out <- simulate_point_estimate_m(simulations = n_sim,
                                             true_N = N,
                                             true_M = M,
                                             m = m_val)
        results_all <- rbind(results_all,
                             data.frame(m = m_val,
                                        true_N = N,
                                        true_M = M,
                                        mse_N_HG = sim_out$MSE_Hypergeometric$N,
                                        mse_M_HG = sim_out$MSE_Hypergeometric$M,
                                        mse_N_NHG = sim_out$MSE_Negative_Hypergeometric$N,
                                        mse_M_NHG = sim_out$MSE_Negative_Hypergeometric$M,
                                        mse_N_ratio = sim_out$MSE_ratio$mse_N_ratio,
                                        mse_M_ratio = sim_out$MSE_ratio$mse_M_ratio))
      }
    }
    
  } else if (m_val == 20) {
    N_vals <- c(450, 600, 800, 1000)
    for (N in N_vals) {
      # Define M values based on N for m = 20
      if (N == 450) {
        M_vec <- seq(30, 150, by = 10)
      } else if (N == 600) {
        M_vec <- seq(30, 200, by = 10)
      } else if (N == 800) {
        M_vec <- seq(30, 250, by = 10)
      } else if (N == 1000) {
        M_vec <- seq(30, 300, by = 10)
      }
      
      for (M in M_vec) {
        sim_out <- simulate_point_estimate_m(simulations = n_sim,
                                             true_N = N,
                                             true_M = M,
                                             m = m_val)
        results_all <- rbind(results_all,
                             data.frame(m = m_val,
                                        true_N = N,
                                        true_M = M,
                                        mse_N_HG = sim_out$MSE_Hypergeometric$N,
                                        mse_M_HG = sim_out$MSE_Hypergeometric$M,
                                        mse_N_NHG = sim_out$MSE_Negative_Hypergeometric$N,
                                        mse_M_NHG = sim_out$MSE_Negative_Hypergeometric$M,
                                        mse_N_ratio = sim_out$MSE_ratio$mse_N_ratio,
                                        mse_M_ratio = sim_out$MSE_ratio$mse_M_ratio))
      }
    }
  }
}
```

```{r}
#| eval: false

write.csv(results_all, file.path("/Users/rachelroggenkemper/Documents/NegativeHypergeometric/Simulation_Comparison", "point_estimate_simulation.csv"), row.names = FALSE)
```

```{r}
#| message: false

point_estimation_sim_df <- read_csv(here::here("Simulation_Comparison", "point_estimate_simulation.csv"))

point_estimation_sim_df <- point_estimation_sim_df %>%
  mutate(M_over_N = true_M / true_N) %>%
  filter(mse_N_ratio <= 2) %>%
  filter(mse_M_ratio <= 2)
```

### MSE (N) Plot 

```{r}
ggplot(point_estimation_sim_df, 
       aes(x = M_over_N, y = mse_N_ratio, 
           color = factor(true_N), group = factor(true_N))) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 1, color = "red", linetype = "dashed") + 
  facet_wrap(~ m, scales = "free_x") +
  labs(title = "MSE N Ratio by M/N",
       x = "M/N",
       y = "MSE N Ratio",
       color = "True N") +
  theme_minimal()
```

### MSE (M) Plot 

```{r}
ggplot(point_estimation_sim_df, 
       aes(x = M_over_N, y = mse_M_ratio, 
           color = factor(true_N), group = factor(true_N))) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 1, color = "red", linetype = "dashed") + 
  facet_wrap(~ m, scales = "free_x") +
  labs(title = "MSE M Ratio by M/N",
       x = "M/N",
       y = "MSE M Ratio",
       color = "True N") +
  theme_minimal()
```
